---
title: "PMOD_reformat_SCH23390"
author: "Jonathan Tjerkaski"
date: "14 June 2019"
output: 
  pdf_document:
    toc: yes
    toc_depth: 3
  md_document:
    toc: yes
    toc_depth: 3
    variant: markdown_github
---

# Libraries

## CRAN libraries

First, the libraries for the analysis and plotting are loaded.

```{r cran_packages, warning=FALSE, message=FALSE}
library(tidyverse)
library(stringr)
library(corrplot)
library(grid)
library(gridExtra)
library(RColorBrewer)
library(psych)
library(readxl)
library(pracma)
library(lme4)
library(rjags)
library(knitr)
library(cowplot)
library(corrplot)
library(viridis)

```

### Loading Non_CRAN libraries and setting theme

```{r load_github_packages, message=FALSE}

library(kinfitr)
library(vmisc)
library(kipettools)
library(granviller)
library(relfeas)

theme_set(theme_light())
```

# Extracting kinfitresults

```{r Extracting_kinfitresults, eval=FALSE}


 tactibble <- tibble(Filename = list.files(path = "../RawData/", 
                                           pattern = "kinfitresults.mat")) %>% 
  group_by(Filename) %>% 
  mutate(tacdata = map(Filename, ~kipettools::kfresults_getData(
    paste0("../RawData/", .x))))

saveRDS(tactibble, '../DerivedData/tactibble.rds')


```

# Tidying data. 

```{r Tidying_data}

#loading data

tacs <- readRDS('../DerivedData/tactibble.rds')

tacs <- tacs %>% 
  ungroup() %>% 
  mutate(Subjname = map_chr(tacdata, "Subjname"),
         PETNo = map_dbl(tacdata, "PETNo"),
         tacdata = map(tacdata, "tacdata")) %>% 
  select(-Filename) 

   

```


```{r}

regions <- c("STR" = "FSLSSTR", "FC" = "FSLSFC", "WB","CBL" = "gmCBL",        "TC" = "FSLSTC", "THA" = "FSLSTHA")
 
tacs <- tacs %>% 
  select(tacdata, Subjname, PETNo) %>% 
  mutate(tacdata = map(tacdata, ~select(.x, regions, times, durations, weights))) 

tacs_long <- tacs %>% 
  unnest(tacdata) %>% 
  mutate(PET = paste(Subjname, PETNo, sep='_')) 

```

# Start time, End time and removing first row

```{r}

#Removing first row

tacs_long <- tacs_long %>% 
  group_by(PET) %>% 
  slice(-1) %>% 
  ungroup()

#Converting units from minutes to seconds

tacs_long <- tacs_long %>% 
  mutate(times = times * 60) %>% 
  mutate(durations = durations * 60)

#Creating start time and end time

tacs_long <- tacs_long %>% 
  mutate("start[seconds]" = times - (durations/2)) %>% 
  mutate("end[nCi/cc]" = times + (durations/2))

#Select Start, End and the region tacs for PMOD. also, keep PET column for ID

tacs_long <-  tacs_long %>% 
  select(`start[seconds]`, `end[nCi/cc]`, STR:THA, PET)
  

```

#Saving each individuals TAC into a seperate excel file according to the PMOD 


```{r}

#Group by and nest

tacs_long <- tacs_long %>% 
  mutate(PET = paste( PET, "tac", sep='_')) %>% 
  group_by(PET) %>% 
  nest(.key = tac)

#Create a named list with PET as the name and the nested data frames as content

TAC <- as.list(tacs_long$tac)
names(TAC) <- tacs_long$PET

#Create a new directory for the .csv files

#dir.create("../PMOD_SCH23390")

dir <- "../PMOD_SCH23390"

#use purr with write_csv

# TAC %>% 
  # names(.) %>% 
  # map(~ write_csv(TAC[[.]], file.path(dir, paste0(., ".csv")))) 

```


#Creating .txt files

```{r eval = FALSE}

oldwd <- getwd()

dir.create("../txt_PMOD_SCH23390")

txt_dir <- "../txt_PMOD_SCH23390"

setwd(txt_dir)

map2(.x = tacs_long$tac, .y = tacs_long$PET, .f = ~ write.table(x = .x, file = paste0(.y, ".txt") , quote = FALSE, row.names = F))

setwd(oldwd)

```

Note: got some strange message "[[1]]NULL" when generating the text files, but the files themselves look fine

#Creating tab delimited files

```{r eval = FALSE}

oldwd <- getwd()

dir.create("../tab_delim_PMOD_SCH23390")

tab_dir <- "../tab_delim_PMOD_SCH23390"

setwd(tab_dir)

map2(.x = tacs_long$tac, .y = tacs_long$PET, .f = ~ write.table(x = .x, file = paste0(.y, ".txt") , quote = FALSE, sep="\t", row.names = F))

setwd(oldwd)

```

Note: got some strange message "[[1]]NULL" when generating the text files, but the files themselves look fine. SAME AS ABOVE.
